---
title: "GitHub Actions"
---

This Quarto website was rendered on GitHub **`{r} Sys.time()` at `{r} Sys.timezone()`**.

In the following I test R code to:

1. Read public shared googlesheet from Google Drive
1. Read googlesheet from private Google Drive
1. Download and read file (.rds) from private Google Drive
1. Write and upload file (.rds) to private Google Drive
1. Read data from external API


Read public shared googlesheet from Google Drive
```{r}
#| echo: true
#| warning: false
#| eval:  true

library(googlesheets4)
library(gt)

googlesheets4::gs4_deauth()     # Without auth

spreadsheet_url <- "https://docs.google.com/spreadsheets/d/1dnzTx2TIxk-QpoWNz08Jr_e4F2rZ4mDBgphzq9lwdYM/edit?usp=drive_link"
data <- googlesheets4::read_sheet(spreadsheet_url, range = "Ark1!A1:D5")
data |> gt()
```


Read googlesheet from private Google Drive
```{r}
#| echo: true
#| warning: false
#| eval: false

library(googledrive)
library(googlesheets4)
library(dplyr)
library(gt)


# Google Authentication
googledrive::drive_auth(
  scopes = "https://www.googleapis.com/auth/drive.readonly")
gs4_auth(token = drive_token())

# Get Google Sheet ID
ss <- googledrive::drive_get("hv8_planter_sheet")

# ss can be url???
# Read data from Google Sheet
data <- googlesheets4::read_sheet(ss, sheet = "content")

data |> gt()
```


Download and read file (.rds) from private Google Drive
```{r}
#| echo: true
#| warning: false
#| eval: false




```


Write and upload file (.rds) to private Google Drive
```{r}
#| echo: true
#| warning: false
#| eval: false




```


Read data from external API: [The Star Wars API](https://swapi.dev/)
```{r}
#| echo: true
#| warning: false
#| eval: true

library(httr2)
library(tidyr)
library(gt)

resp_json <- 
  httr2::request("https://swapi.dev/api/people/") |>
  httr2::req_perform() |>
  httr2::resp_body_json(simplifyVector = TRUE)

name_people <- 
  resp_json$results$name |>  tidyr::as_tibble()
name_people |> gt()
```



